A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2022-10-17 kobakian-cook.tex
paper compiles nicely

Many cancer atlases present geospatial cancer data on a choropleth map
display. The Australian Cancer Atlas \citep{TACA} is a recent addition
to the many cancer atlas maps worldwide. The ground-breaking atlas for
Australia presents a central map that shows the landmass overlaid with
administrative boundaries. This choropleth display can highlight the
geographic patterns in geospatially related cancer statistics
\citep{SAMGIS}.

Over time, the density of living in major cities has increased as
residents have gathered to live near urban areas \citep{ACTUC}. The
division of these residents into approximately equal population areas
results in dramatically different square meterage of administrative
geographic units, such as states or electorates. In a choropleth map
display, the geographic units are coloured to represent the value of the
statistic for each unit \citep{EI}. This can cause some values to be
emphasised over others, and allows choropleth map displays to
misrepresent the spatial distributions of human related statistics due
to area-size bias \citep{BCM}. Figure \ref{fig:choro} is a choropleth
map that uses colour to display the estimated standardised incidence
ratios (SIRs) of thyroid cancer for females, in each of the Statistical
Areas at Level 2 (SA2) used by the \citet{abs2011}. The Australian
choropleth map display draws attention to the expanse of dark and light
blue areas across the rural communities in all states. The SA2s on the
east coast around Brisbane and in northern New South Wales stand out as
more orange and red. However, this display neglects the vast amount of
Australia residents living in the densely populated capital cities.

\begin{Schunk}
\begin{figure}
\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/choro-1} \caption[A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2]{A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2. Blue indicates lower than average and red indicates higher than average incidence. A cluster of high incidence is visible on the east coast.}\label{fig:choro}
\end{figure}
\end{Schunk}

The solutions to this visualisation problem begin with the geography.
Alternative maps can be created to shift the focus from land area and
shape to the value of the statistics \citep{ACCAC}. Each style of
cartogram applies a different transformation to the geographic areas, to
highlight the values of the statistic of interest. Alternative maps can
result in a distortion of the map space to represent features of the
distribution across the areas \citep{ACCAC} as the statistic of interest
is used to determine the cartogram layout.

Alternative mapping methods, like cartograms implemented in
\CRANpkg{cartogram}, allow increased understanding of the spatial
distribution of a variable across the population, by fairly representing
the population in each administrative area \citep{TAAM}. This
acknowledges that the number of residents can be different and also
recognises that each area, or person within it is equally important.

@@

The familiar choropleth map display is often used to allow the user to
orient themselves. However, the emphasis on the land mass diminishes the
features of the distribution in densely populated communities due to the
small size on the display \citep{ACTUC}. The unique shapes of boundaries
can be helpful for orienting users but may not contribute to their
understanding of the spatial disease distribution as many of the
communities are not visible in a choropleth display \citep{TVSSS}.

Administrative areas are often used to aggregate census data and used to
understand demographics within communities of the Australian population.
Each SA2 \citep{abs2011} was designed to represent a community. This
collection of communities presents an opportunity for explicit map
transformations to improve communication of spatial distributions
\citep{CBATCC}. In Figure \ref{fig:tasdisplays} the choropleth map can
be seen underneath each alternative map display to allow for comparisons
to be made.

There are several established alternative visualisation methods.
Rectangular cartograms \citep{ORC} and Dorling cartograms \citep{ACTUC}
implemented in \pkg{cartogram} and tile maps implemented in
\CRANpkg{tilemaps}, all use one simple shape to represent each
geographic unit. They all minimise the emphasis on the size or shape of
the geographic areas. These alternative map displays focus on the
relationship between neighbours, attempting to preserve connections, and
disregard the unique shapes of the administrative boundaries. Figure
\ref{fig:tasdisplays} shows a collection of alternative map displays,
this includes a) a contiguous cartogram, b) a non-contiguous cartogram,
and c) a Dorling cartogram.

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{kobakian-cook_files/figure-latex/tasdisplays-1} \caption[The three displays show alternative maps of the Australian state of Tasmania at SA2 level]{The three displays show alternative maps of the Australian state of Tasmania at SA2 level: (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania. The contiguous cartogram looks like the state has an hourglass figure, while the non-contiguous cartogram shrinks areas into invisibility. The Dorling expands the metropolitan regions.}\label{fig:tasdisplays}
\end{figure}
\end{Schunk}

When communicating information that is relevant to the population, each
member of the population can be given equal representation by
transforming the map \citep{TVSSS}. The connected communities can be
recognised by allowing the boundaries to maintain connection in the
transformed display. The contiguous cartogram displayed in Figure
\ref{fig:tasdisplays}a draws attention to smaller geographic units when
they are rescaled according to the population \citep{DMAHP}. These new
shapes can now be coloured to represent a second variable. The algorithm
uses the geographic shape of the areas and iterates toward sizing the
areas to represent the population. This display can create twisted and
unfamiliar shapes from the geographic units as the algorithms must
satisfy the topology conditions, especially when there are communities
located geographically far from their neighbours \citep{TVSSS}.

The non-contiguous cartogram in Figure \ref{fig:tasdisplays}b also uses
the population to rescale the geographic units. Unlike the contiguous
cartogram, the SA2 areas maintain their geographic shape, but they may
not retain the connection with their neighbours. The population of the
SA2 areas is used to scale the geographic units in the non-contiguous
cartogram \citep{NAC}. The amount of background space can be meaningful
in non-contiguous cartograms \citep{ECGC}. The size disparity between
rural areas and urban areas result in reasonable display within the
south eastern city of Hobart, but these units are not visible in the
context of the Tasmania state map. Depending on the difference between
the population and geographic land size, the amount of white space can
also prevent meaningful understanding of the distribution \citep{TVSSS}.

The Dorling cartogram presents each geographic unit as a circle, the
size of the circle is scaled according to the population value of each
area \citep{ACTUC}. Figure \ref{fig:tasdisplays}c shows the Tasmania SA2
areas as an individual circle located as close as possible to the
geographic centroid location. This map draws attention to the collection
of coastal cities in Tasmania that were not apparent in Figure
\ref{fig:tasdisplays} a or b. This display also highlights that the
approximation of equal population is not easy to fulfil, as there is
some disparity in the sizes of the circles.

It is also common to treat all geographic units as equal, so that
regardless of the population or other information, to generate equal
size spatial polygons. The Dorling algorithm can be induced to do this,
to make equallly sized circles. \citet{MDAC} describes a group of
alternative maps called ``mosaic cartograms'' for tile displays. The
geography of the USA has been transformed into a square-binned tile map
manually and made available in the R package \CRANpkg{statebins}
\citep{statebins}.The algorithm described below is an automatic layout
of hexagon tiles, where a continguity constraint is relaxed. This gives
equal weight to each geographic area even if the population differs.

@@

The algorithm is implemented in the \pkg{sugarbag} package for
\texttt{R}, named after the common name for the \emph{Trigona
carbonaria} bee -- a species which builds flat layers of hexagonal brood
cells, spiralling out from a central point \citep{PH}. This unusual
pattern also provided the inspiration for the algorithm, where the maps
are constructed by building out from multiple focal points on the
geographic map base in a spiral fashion.

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/hexmap-1} \caption[A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1]{A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1. The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots.}\label{fig:hexmap}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{figs/sugarbag_flow} \caption[A flow diagram detailing the steps taken to create a hexagon tile map]{A flow diagram detailing the steps taken to create a hexagon tile map. There are two basic processes, one to make the grid, and the other to allocate centroids to grid points.}\label{fig:sugarbagflow}
\end{figure}
\end{Schunk}

@@

The \pkg{sugarbag} package contains a set of functions that help R users
to create a hexagon tile map. The algorithm presented in the
\pkg{sugarbag} package operates on a set of simple feature geometry
objects , known as \CRANpkg{sf} objects\citep{sf}. This package allows R
users to create \pkg{sf} objects by importing polygons stored in various
formats. Users should provide a set of polygons that define geographic
units by their administrative boundaries. The functions arrange the
geographic units in order of proximity to a set of locations provided,
such as the centre of major cities. The centroid location of each
geographic unit is used to measure the proximity. It emphasises the
major cities as population hubs, rather than emphasizing the size of
large, rural geographic units.

@@

\begin{Schunk}
\begin{Sinput}
install.packages("sugarbag")
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
devtools::install_github("srkobakian","sugarbag")
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Illustration of key steps of the algorithm]{Illustration of key steps of the algorithm: (1a) full hexagon grid is created first; (1b) buffer is applied, shown as dark green circles, to accommodate irregularly shaped regions; (2a, 2b) allocation process, relative the center of Hobart, showing the 8th centroid to be allocated. The relationship between Hobart (the cross) and the centroid (the purple triangle) is used to filter the potential locations from the grid within a wedge. Hexagons already allocated are shown in black, and the purple circle indicates the hexagon to be assigned to the 8th centroid.}\label{fig:filterprocess}
\end{figure}
\end{Schunk}

@@

Creating an animation connecting these two displays can allow users to
grasp the meaning of the connected hexagons. It will also highlight the
density of the communities using the rapid expansion of the inner-city
areas, these hexagons will move the furthest and will move rapidly in
the animation from their geographic locations. The rapid decrease in
size of the large rural areas can show the large size of their
collective landmass. The \CRANpkg{gganimate} \citep{gganimate} package
can be used to make an animation. It connects the polygons for each area
in the two displays using the \code{sf\_id} variable, the names of the
statistical areas, and creates intermediate displays as they geographic
areas shrink or expand to the chosen hexagon size.

@@

@@

\address{%
Stephanie Kobakian\\
Monash University\\%
Department of Econometrics and Business Statistics\\
%
%
%
\href{mailto:stephanie.kobakian@monash.edu}{\nolinkurl{stephanie.kobakian@monash.edu}}%
}

>>>>

Many cancer atlases present geospatial cancer data on a choropleth map display. The Australian Cancer Atlas (Cancer Council Queensland, Queensland University of Technology, and Cooperative Research Centre for Spatial Information 2018) is a recent addition to the many cancer atlas maps worldwide. The ground-breaking atlas for Australia presents a central map that shows the landmass overlaid with administrative boundaries. This choropleth display can highlight the geographic patterns in geospatially related cancer statistics (Moore and Carpenter 1999).

Over time, the density of living in major cities has increased as residents have gathered to live near urban areas (Dorling 2011). The division of these residents into approximately equal population areas results in dramatically different square meterage of administrative geographic units, such as states or electorates. In a choropleth map display, the geographic units are coloured to represent the value of the statistic for each unit (Tufte 1990). This can cause some values to be emphasised over others, and allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias (Skowronnek 2016).

The Australian Cancer Atlas is an online, interactive display of Australian cancer statistics in each of the Statistical Areas at Level 2 (SA2s), used by the Australian Bureau of Statistics (2011). The estimated standardised incidence ratios (SIRs) of thyroid cancer
for females was downloaded from the publicly accessible Australian Cancer Atlas website and presented in Figure \ref{fig:choro}, a choropleth map that uses colour to display the distribution. The Australian choropleth map display draws attention to the expanse of dark and light blue areas across the rural communities in all states. The SA2s on the east coast around Brisbane and in northern New South Wales stand out as more orange and red. However, this display neglects the vast amount of Australia residents living in the densely populated capital cities.

\begin{figure}
\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/choro-1} \caption{A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2. Blue indicates lower than average and red indicates higher than average incidence. A cluster of high incidence is visible on the east coast.}\label{fig:choro}
\end{figure}

The solutions to this visualisation problem begin with the geography. Alternative maps can be created to shift the focus from land area and shape to the value of the statistics (Dougenik, Chrisman, and Niemeyer 1985). Each style of cartogram applies a different transformation to the geographic areas, to highlight the values of the statistic of interest. Alternative maps can result in a distortion of the map space to represent features of the distribution across the areas (Dougenik, Chrisman, and Niemeyer 1985) as the statistic of interest is used to determine the cartogram layout.

Alternative mapping methods, like cartograms implemented in \CRANpkg{cartogram}, allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area (Levison and Haddon Jr 1965). This acknowledges that the number of residents can be different and also recognises that each area, or person within it is equally important.

@@

The familiar choropleth map display is often used to allow the user to orient themselves. However, the emphasis on the land mass diminishes the features of the distribution in densely populated communities due to the small size on the display (Dorling 2011). The unique shapes of boundaries can be helpful for orienting users but may not contribute to their understanding of the spatial disease distribution as many of the communities are not visible in a choropleth display (Dorling 2012).

Administrative areas are often used to aggregate census data and used to understand demographics within communities of the Australian population. Each SA2 (Australian Bureau of Statistics 2011) was designed to represent a community. This collection of communities presents an opportunity for explicit map transformations to improve communication of spatial distributions (Kocmoud and House 1998). In Figure \ref{fig:tasdisplays} the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.

There are several established alternative visualisation methods. Rectangular cartograms (Kreveld and Speckmann 2007) and Dorling cartograms (Dorling 2011) implemented in \pkg{cartogram} and tile maps implemented in \CRANpkg{tilemaps}, all use one simple shape to represent each geographic unit. They all minimise the emphasis on the size or shape of the geographic areas. These alternative map displays focus on the relationship between neighbours, attempting to preserve connections, and disregard the unique shapes of the administrative boundaries. Figure \ref{fig:tasdisplays} shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, and c) a Dorling cartogram.

\begin{figure}
\includegraphics[width=1\linewidth]{kobakian-cook_files/figure-latex/tasdisplays-1} \caption{The three displays show alternative maps of the Australian state of Tasmania at SA2 level: (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania. The contiguous cartogram looks like the state has an hourglass figure, while the non-contiguous cartogram shrinks areas into invisibility. The Dorling expands the metropolitan regions.}\label{fig:tasdisplays}
\end{figure}

When communicating information that is relevant to the population, each member of the population can be given equal representation by transforming the map (Dorling 2012). The connected communities can be recognised by allowing the boundaries to maintain connection in the transformed display. The contiguous cartogram displayed in Figure \ref{fig:tasdisplays}a draws attention to smaller geographic units when they are rescaled according to the population (Walter 2001). These new shapes can now be coloured to represent a second variable. The algorithm uses the geographic shape of the areas and iterates toward sizing the areas to represent the population. This display can create twisted and unfamiliar shapes from the geographic units as the algorithms must satisfy the topology conditions, especially when there are communities located geographically far from their neighbours (Dorling 2012).

The non-contiguous cartogram in Figure \ref{fig:tasdisplays}b also uses the population to rescale the geographic units. Unlike the contiguous cartogram, the SA2 areas maintain their geographic shape, but they may not retain the connection with their neighbours. The population of the SA2 areas is used to scale the geographic units in the non-contiguous cartogram (Olson 1976). The amount of background space can be meaningful in non-contiguous cartograms (Keim et al. 2002). The size disparity between rural areas and urban areas result in reasonable display within the south eastern city of Hobart, but these units are not visible in the context of the Tasmania state map. Depending on the difference between the population and geographic land size, the amount of white space can also prevent meaningful understanding of the distribution (Dorling 2012).

The Dorling cartogram presents each geographic unit as a circle, the size of the circle is scaled according to the population value of each area (Dorling 2011). Figure \ref{fig:tasdisplays}c shows the Tasmania SA2 areas as an individual circle located as close as possible to the geographic centroid location. This map draws attention to the collection of coastal cities in Tasmania that were not apparent in Figure \ref{fig:tasdisplays} a or b. This display also highlights that the approximation of equal population is not easy to fulfil, as there is some disparity in the sizes of the circles.

It is also common to treat all geographic units as equal, so that regardless of the population or other information, to generate equal size spatial polygons. The Dorling algorithm can be induced to do this, to make equallly sized circles. Cano et al. (2015) describes a group of alternative maps called ``mosaic cartograms'' for tile displays. The geography of the USA has been transformed into a square-binned tile map manually and made available in the R package \CRANpkg{statebins} (Rudis 2020).The algorithm described below is an automatic layout of hexagon tiles, where a continguity constraint is relaxed. This gives equal weight to each geographic area even if the population differs.

@@

The algorithm is implemented in the \pkg{sugarbag} package for \texttt{R}, named after the common name for the \emph{Trigona carbonaria} bee -- a species which builds flat layers of hexagonal brood cells, spiralling out from a central point (Vit, Pedro, and Roubik 2013). This unusual pattern also provided the inspiration for the algorithm, where the maps are constructed by building out from multiple focal points on the geographic map base in a spiral fashion.

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/hexmap-1} \caption{A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1. The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots.}\label{fig:hexmap}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{figs/sugarbag_flow} \caption{A flow diagram detailing the steps taken to create a hexagon tile map. There are two basic processes, one to make the grid, and the other to allocate centroids to grid points.}\label{fig:sugarbagflow}
\end{figure}

@@

The \pkg{sugarbag} package contains a set of functions that help R users to create a hexagon tile map. The algorithm presented in the \pkg{sugarbag} package operates on a set of simple feature geometry objects , known as \CRANpkg{sf} objects(Pebesma 2018). This package allows R users to create \pkg{sf} objects by importing polygons stored in various formats. Users should provide a set of polygons that define geographic units by their administrative boundaries. The functions arrange the geographic units in order of proximity to a set of locations provided, such as the centre of major cities. The centroid location of each geographic unit is used to measure the proximity. It emphasises the major cities as population hubs, rather than emphasizing the size of large, rural geographic units.

@@

\begin{verbatim}
install.packages("sugarbag")
\end{verbatim}

@@

\begin{verbatim}
devtools::install_github("srkobakian","sugarbag")
\end{verbatim}

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption{Illustration of key steps of the algorithm: (1a) full hexagon grid is created first; (1b) buffer is applied, shown as dark green circles, to accommodate irregularly shaped regions; (2a, 2b) allocation process, relative the center of Hobart, showing the 8th centroid to be allocated. The relationship between Hobart (the cross) and the centroid (the purple triangle) is used to filter the potential locations from the grid within a wedge. Hexagons already allocated are shown in black, and the purple circle indicates the hexagon to be assigned to the 8th centroid.}\label{fig:filterprocess}
\end{figure}

@@

Creating an animation connecting these two displays can allow users to grasp the meaning of the connected hexagons. It will also highlight the density of the communities using the rapid expansion of the inner-city areas, these hexagons will move the furthest and will move rapidly in the animation from their geographic locations. The rapid decrease in size of the large rural areas can show the large size of their collective landmass. The \CRANpkg{gganimate} (Pedersen and Robinson 2019) package can be used to make an animation. It connects the polygons for each area in the two displays using the \code{sf\_id} variable, the names of the statistical areas, and creates intermediate displays as they geographic areas shrink or expand to the chosen hexagon size.

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-abs2011}{}}%
Australian Bureau of Statistics. 2011. {``{Statistical Area Level 2 (SA2) ASGS Ed 2011 Digital Boundaries in ESRI Shapefile Format}.''} data cube: ESRI Shapefile, cat. no. 1270.0.55.001. 2011.

\leavevmode\vadjust pre{\hypertarget{ref-TACA}{}}%
Cancer Council Queensland, Queensland University of Technology, and Cooperative Research Centre for Spatial Information. 2018. {``{Australian Cancer Atlas}.''} \url{https://atlas.cancer.org.au}.

\leavevmode\vadjust pre{\hypertarget{ref-MDAC}{}}%
Cano, R. G., K. Buchin, T. Castermans, A. Pieterse, W. Sonke, and B. Speckmann. 2015. {``{Mosaic Drawings and Cartograms}.''} In \emph{Computer Graphics Forum}, 34:361--70. 3. Wiley Online Library.

\leavevmode\vadjust pre{\hypertarget{ref-ACTUC}{}}%
Dorling, Daniel. 2011. {``Area Cartograms: Their Use and Creation.''} In \emph{Concepts and Techniques in Modern Geography (CATMOG)}, 59:252--60. \url{https://doi.org/10.1002/9780470979587.ch33}.

\leavevmode\vadjust pre{\hypertarget{ref-TVSSS}{}}%
---------. 2012. \emph{{The Visualisation of Spatial Social Structure}}. John Wiley; Sons Ltd.

\leavevmode\vadjust pre{\hypertarget{ref-ACCAC}{}}%
Dougenik, James A., Nicholas R. Chrisman, and Duane R. Niemeyer. 1985. {``{An Algorithm to Construct Continuous Area Cartograms}.''} \emph{The Professional Geographer} 37 (1): 75--81. \url{https://doi.org/10.1111/j.0033-0124.1985.00075.x}.

\leavevmode\vadjust pre{\hypertarget{ref-ECGC}{}}%
Keim, D. A, S. C North, C Panse, and J Schneidewind. 2002. {``{Efficient Cartogram Generation: A Comparison}.''} In \emph{{IEEE Symposium on Information Visualization, 2002. INFOVIS 2002}}, 2002:33--36. IEEE.

\leavevmode\vadjust pre{\hypertarget{ref-CBATCC}{}}%
Kocmoud, C, and D House. 1998. {``{A Constraint-based Approach to Constructing Continuous Cartograms}.''} In \emph{Proc. Symp. Spatial Data Handling}, 236--46.

\leavevmode\vadjust pre{\hypertarget{ref-ORC}{}}%
Kreveld, Marc van, and Bettina Speckmann. 2007. {``On {R}ectangular {C}artograms.''} \emph{{Computational Geometry}} 37 (3): 175--87. \url{https://doi.org/10.1016/j.comgeo.2006.06.002}.

\leavevmode\vadjust pre{\hypertarget{ref-TAAM}{}}%
Levison, M. E., and W. Haddon Jr. 1965. {``{The Area Adjusted Map. An Epidemiologic Device}.''} Journal Article. \emph{Public Health Reports} 80: 55--59.

\leavevmode\vadjust pre{\hypertarget{ref-SAMGIS}{}}%
Moore, Dale A., and Tim E. Carpenter. 1999. {``{Spatial Analytical Methods and Geographic Information Systems: Use in Health Research and Epidemiology}.''} \emph{Epidemiologic Reviews} 21 (2): 143--61. \url{https://doi.org/10.1093/oxfordjournals.epirev.a017993}.

\leavevmode\vadjust pre{\hypertarget{ref-NAC}{}}%
Olson, Judy M. 1976. {``{Noncontiguous Area Cartograms}.''} \emph{The Professional Geographer} 28 (4): 371--80. \url{https://doi.org/10.1111/j.0033-0124.1976.00371.x}.

\leavevmode\vadjust pre{\hypertarget{ref-sf}{}}%
Pebesma, Edzer. 2018. {``{Simple Features for R: Standardized Support for Spatial Vector Data}.''} \emph{{The R Journal}} 10 (1): 439--46. \url{https://doi.org/10.32614/RJ-2018-009}.

\leavevmode\vadjust pre{\hypertarget{ref-gganimate}{}}%
Pedersen, Thomas Lin, and David Robinson. 2019. \emph{{gganimate: A Grammar of Animated Graphics}}. \url{https://CRAN.R-project.org/package=gganimate}.

\leavevmode\vadjust pre{\hypertarget{ref-statebins}{}}%
Rudis, Bob. 2020. \emph{Statebins: Create United States Uniform Cartogram Heatmaps}. \url{https://CRAN.R-project.org/package=statebins}.

\leavevmode\vadjust pre{\hypertarget{ref-BCM}{}}%
Skowronnek, Alsino. 2016. {``{Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata}.''} {Infovis Reading Group WS 2015/16}. 2016. \url{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}.

\leavevmode\vadjust pre{\hypertarget{ref-EI}{}}%
Tufte, Edward R. 1990. \emph{Envisioning Information}. Graphics Press.

\leavevmode\vadjust pre{\hypertarget{ref-PH}{}}%
Vit, Patricia, Silvia R. M. Pedro, and David Roubik. 2013. \emph{{Pot-Honey: A legacy of stingless bees}}. Springer-Verlag New York. \url{http://dx.doi.org/10.1007/978-1-4614-4960-7}.

\leavevmode\vadjust pre{\hypertarget{ref-DMAHP}{}}%
Walter, S. D. 2001. \emph{{Disease Mapping: A Historical Perspective}}. Oxford University Press. https://doi.org/\url{https://dx.doi.org/10.1093/acprof:oso/9780198515326.003.0012}.

\end{CSLReferences}

@@

\address{%
Stephanie Kobakian\\
\\%
Sydney, Australia\\
%
%
%
\href{mailto:stephanie.kobakian@gmail.com}{\nolinkurl{stephanie.kobakian@gmail.com}}%
}
